Reducing iptables configuration complexity using chains

### 2014-03-30 iptables/presentation.tex
rename iptables presentation

>>>>

    \frametitle{Intermezzo : firewall on your PC}
    Protect your own PC, block all incoming requests :
      iptables -P OUTPUT ACCEPT}\\
      \small{iptables -A INPUT -i lo -j ACCEPT \# allow local traffic\\
      iptables -A INPUT -p icmp -j ACCEPT \# allow ping\\
      iptables -A INPUT -m state --state ESTABLISHED,RELATED -j ACCEPT}
    Add ESTABLISHED, to allow replies of outgoing connections you intiated!
